### 2022-06-13 main/chapter_2ljets.tex
clarify low, mention 2jet selection

Angular selections on lepton variables $\rll$ and $\dphillmet$ are used to
reject $\ttbar$ and provide signal sensitivity in Low regions, which are
defined in Table~\ref{tab:2ljets_low}.
Motivations for these angular selections are displayed in
Figure~\ref{fig:2ljets_low_minus}, and discussed here.

@@

\subsubsection{Low-ISR}
\label{sec:2ljets_low_isr}
Figure~\ref{fig:2ljets_low_isr_old}
% TODO

>>>>

Angular selections on lepton variables $\rll$ and $\dphillmet$ characterize
the Low regions, which are defined in Table~\ref{tab:2ljets_low}.
These angular variables usefully reject backgrounds including $\ttbar$, and
provide signal sensitivity to benchmark signal models, as illustrated in
Figure~\ref{fig:2ljets_low_minus};
signals with with small mass splittings of around $100\textrm{--}150\,\eV[G]$
are targetted.

To remove some observed mis-modelling of backgrounds, Low regions require
exactly two jets.
Abandoned region designs which used more jets are discussed below in
Section~\ref{sec:2ljets_low_isr}.

@@

\subsubsection{Low-ISR}
\label{sec:2ljets_low_isr}
Figure~\ref{fig:2ljets_low_isr_old}

The Low regions presented in Section~\ref{sec:2ljets_low_isr} resulted from a
hasty redesign shortly before unblinding.
